Privacy-Preserving Localization Using Private Linear-Combination Aggregation

### 2021-05-31 main.tex
Updated notation section for the updated paper Fixed typo in equation

\subsection{Notation}
Throughout this work, we will use the following notation. Lowercase underlined characters are vectors, $\vec{a}$, and random variables are bold, $\rv{a}$. Uppercase bold characters are matrices, $\mat{A}$, with $\mat{A}^{-1}$ denoting the inverse and $\mat{A}^\top$ the transpose. $|a|$ is the absolute value of $a$ and $\lVert\vec{a}\rVert$ the vector norm. Subscripts of the form $\rv{x}_{k|j}$ will denote an estimate of $\rv{x}_k$ using measurements from times up to and including $j$. $\mathsf{E}[\cdot]$ and $\mathsf{Var}[\cdot]$ are used for the expected value and variance, respectively, and encryption and decryption with key $k$ are denoted $\mathcal{E}_{k}(\cdot)$ and $\mathcal{D}_{k}(\cdot)$. Additionally, key $k$ may be ommited when inferrable from context. $\lfloor\cdot\rceil$ rounds to the nearest integer, $a\|b$ stands for a bitwise concatenation of $a$ and $b$ and sets will be written as $\{\dots\}$ while ordered sequences as $\langle\dots\rangle$.

@@

Computing $z'_{k,i}$ and its variance $r_{k,i}$ from the original measurements $z_{k,i}$ are complicated by the noise term $v_{k,i} \sim \mathcal{N}(0, r_i)$, and simply squaring the original range measurements produces
\begin{equation}
    \begin{split}
        z_{k,i}^2 &= (h_i(\vec{x}_k) + v_{k,i})^2 \\
        &= h'_i(\vec{x}_k) + 2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2\,,
    \end{split}
\end{equation}
with a new noise term $2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2$, now dependent on the measurement function $h_i$, and no longer zero-mean. We can compute the mean of this new noise term (a function of the Gaussian term $v_{k,i}$) as
\begin{equation}
    \mathsf{E}[2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2] = r_i\, \label{eqn:modified_noise_mean}
\end{equation}
and mean-adjust modified measurements as
\begin{equation}
    \begin{split}
        z'_{k,i} &= z_{k,i}^2 - r_i \\
        &= h_i(\vec{x}_k)^2 + 2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2 - r_i \\
        &= h'_i(\vec{x}_k) + v'_{k,i}\,,
    \end{split} \label{eqn:modified_measurement}
\end{equation}
with now zero-mean noise $v'_{k,i} = 2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2 - r_i$. The noise in this case (again a function of Gaussian term $v_{k,i}$) has variance 
\begin{equation}
    \mathsf{Var}[v'_{k,i}] = 4h_i(\vec{x}_k)^2r_i + 2r_i^2
\end{equation}
and is also dependent on $h_i$. To use the modified measurement \eqref{eqn:modified_measurement} with the EIF, we require an estimate for $\mathsf{Var}[v'_{k,i}]$ at the sensor as well. Additionally, a conservative estimate (\textit{i.e.}, a larger variance resulting in less confidence in measurements) is desirable to reduce filter divergence. The naive approach, replacing $h_i(\vec{x}_k)$ with $z_{k,i}$, only provides a conservative estimate when
\begin{equation}
    \begin{split}
        &z_{k,i} > h_i(\vec{x}_k) \\
        \implies &v_{k,i} > 0\,,
    \end{split}
\end{equation}
which cannot be guaranteed. Instead, we provide a conservative estimate with $95\%$ confidence due to the Gaussianity of $v_{k,i}$, by adjusting the replacement term $z_{k,i}$ by two of its standard deviations $\sqrt{r_i}$. The modified measurement's variance at timestep $k$ is therefore conservatively approximated by
\begin{equation}
    \begin{split}
        r_{k, i} &= 4(z_{k,i} + 2\sqrt{r_i})^2r_i + 2r_i^2 \\
        &\gtrapprox \Var{v'_{k,i}}
    \end{split}\,. \label{eqn:modified_measurement_variance_estimate}
\end{equation}
at each sensor $i$.

>>>>

\subsection{Notation}
Throughout this work, we make use of the following notation. Underlined characters, $\vec{a}$, denote vectors, uppercase bold characters, $\mat{A}$, denote matrices. $\mat{A}^{-1}$ is the matrix inverse while $\mat{A}^\top$ is its transpose. The expected value of a random variable is denoted $\mathsf{E}[\cdot]$, while the variance of a random scalar and covariance of a random vector by $\mathsf{Var}[\cdot]$ and $\mathsf{Cov}[\cdot]$, respectively. $|a|$ denotes absolute value, $\lVert\vec{a}\rVert$ the vector norm, $\{\dots\}$ is used for sets and $\langle\dots\rangle$ for ordered sequences. When estimating a state, notation $\vec{x}_{k|l}$ will denote an estimate at timestep $k$ given measurements from timesteps up to and including $l$. When discussing cryptography, $\mathcal{E}_{k}(\cdot)$ and $\mathcal{D}_{k}(\cdot)$ will denote encryption and decryption with key $k$, respectively, with $k$ ommited when inferrable from context. $\mathbb{Z}_n$ is used for the set of integers modulo $n$ and $\mathbb{Z}^*_n$ for its multiplicative group. $\mathsf{lcm}(\cdot,\cdot)$ is the lowest common denominator, $\|$ the binary concatination operator, and the term negligible function refers to the cryptographic definition in \cite{katzIntroductionModernCryptography2008}.

@@

Computing $z'_{k,i}$ and its variance $r_{k,i}$ from the original measurements $z_{k,i}$ are complicated by the noise term $v_{k,i} \sim \mathcal{N}(0, r_i)$, and simply squaring the original range measurements produces
\begin{equation}
    \begin{split}
        z_{k,i}^2 &= (h_i(\vec{x}_k) + v_{k,i})^2 \\
        &= h'_i(\vec{x}_k) + 2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2\,,
    \end{split}
\end{equation}
with a new noise term $2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2$, now dependent on the measurement function $h_i$, and no longer zero-mean. We can compute the mean of this new noise term (a function of the Gaussian term $v_{k,i}$) as
\begin{equation}
    \mathsf{E}[2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2] = r_i\, \label{eqn:modified_noise_mean}
\end{equation}
and mean-adjust modified measurements as
\begin{equation}
    \begin{split}
        z'_{k,i} &= z_{k,i}^2 - r_i \\
        &= h_i(\vec{x}_k)^2 + 2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2 - r_i \\
        &= h'_i(\vec{x}_k) + v'_{k,i}\,,
    \end{split} \label{eqn:modified_measurement}
\end{equation}
with now zero-mean noise $v'_{k,i} = 2h_i(\vec{x}_k)v_{k,i} + v_{k,i}^2 - r_i$. The noise in this case (again a function of Gaussian term $v_{k,i}$) has variance 
\begin{equation}
    \mathsf{Var}[v'_{k,i}] = 4h_i(\vec{x}_k)^2r_i + 2r_i^2
\end{equation}
and is also dependent on $h_i$. To use the modified measurement \eqref{eqn:modified_measurement} with the EIF, we require an estimate for $\mathsf{Var}[v'_{k,i}]$ at the sensor as well. Additionally, a conservative estimate (\textit{i.e.}, a larger variance resulting in less confidence in measurements) is desirable to reduce filter divergence. The naive approach, replacing $h_i(\vec{x}_k)$ with $z_{k,i}$, only provides a conservative estimate when
\begin{equation}
    \begin{split}
        &z_{k,i} > h_i(\vec{x}_k) \\
        \implies &v_{k,i} > 0\,,
    \end{split}
\end{equation}
which cannot be guaranteed. Instead, we provide a conservative estimate with $95\%$ confidence due to the Gaussianity of $v_{k,i}$, by adjusting the replacement term $z_{k,i}$ by two of its standard deviations $\sqrt{r_i}$. The modified measurement's variance at timestep $k$ is therefore conservatively approximated by
\begin{equation}
    \begin{split}
        r_{k, i} &= 4(z_{k,i} + 2\sqrt{r_i})^2r_i + 2r_i^2 \\
        &\gtrapprox \mathsf{Var}[v'_{k,i}]
    \end{split}\,. \label{eqn:modified_measurement_variance_estimate}
\end{equation}
at each sensor $i$.
